---
title: "Analysis of the COVID-19 Shock, Technology and Trade"
subtitle: "Regression Results for Mexico, India and Indonesia - Firm-Month Level"
author: "Simón Caicedo"
date: \today
header-includes:
  \usepackage{float}
  \usepackage{placeins}
  \usepackage{rotating}
  \usepackage{graphicx}
  \usepackage{booktabs}
  \usepackage{caption}
  \usepackage{longtable}
  \usepackage{breqn}
output:
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning  = FALSE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

# Set Working Directory ----
fileloc <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(fileloc)
rm(fileloc)


# modelsummary package options----
options("modelsummary_format_numeric_latex" = "plain")


# Libraries to be used ----
source("../src/packages.R")

```

# 1. Does Tech Adoption Affect Trade Outcomes?

These regressions aim to analyze the impact of technology adoption on trade outcomes. The regression model used is as follows:

\begin{equation}\label{reg_1}
    y_{it} = \alpha_0 + \alpha_1 tech_{i,t-l} + FE_i + FE_t + \epsilon_{it} 
\end{equation}


Where $y_{it}$ represents the trade outcome for the firm $i$ in the month $t$. Specifically, the outcomes for the intensive margin regressions can be the logarithm of number of exports/imports of a firm $i$ in the month $t$, the number of sources or destinations of a firm $i$ in a month $t$  or a dummy indicating whether a firm $i$ in a month $t$ is trading with a new source or a new destination. The variable $tech_{i,t-l}$ is a dummy indicating whether the firm $i$ in month $t-l$ ($l$ is the number of lags taken) used an adopted E-commerce or E-payment technology. 

Time fixed-effects control for unobserved variables that are constant at the firm level but vary over time. Firm fixed-effects control for unobserved time-invariant heterogeneities across firms. 

## 1.1 Intensive Margin Analysis


```{r}

# India - intensive margin regressions of the model that measure if tech adoption affects trade outcomes
source("../India/05_regressions_firm_month_level_IND.R", chdir = TRUE)

# Mexico - intensive margin regressions of the model that measure if tech adoption affects trade outcomes
source("../Mexico/05_regressions_firm_month_level_MEX.R", chdir = TRUE)

# Indonesia - intensive margin regressions of the model that measure if tech adoption affects trade outcomes
source("../Indonesia/05_regressions_firm_month_level_IDN.R", chdir = TRUE)


# Remove objects that are not longer needed
rm(import_data_IND, export_data_IND,
   import_data_IDN, export_data_IDN, 
   import_data_MEX, export_data_MEX)

```



```{r, eval=TRUE}

reg_firm_month_IND[[2]]

```



```{r, eval=TRUE}

reg_firm_month_MEX[[2]]

```



```{r, eval=TRUE}

reg_firm_month_IDN[[2]]

```


# 2. Does Existing Tech Use Mitigate COVID Impacts?

The aim of these regressions is to investigate whether companies that had adopted E-payment or E-commerce technology before 2020 were better equipped to mitigate the impacts of COVID on their trade outcomes. The regression model is specified as follows:

\begin{dmath}\label{reg_2}
y_{it} = \alpha_0 + \alpha_1 tech_i \cdot covid_t + FE_i + FE_t + \epsilon_{it}
\end{dmath}

Trade outcomes $y_{it}$ are the same as in equation (1). The variable $tech_i$ is a dummy variable indicating whether the company adopted an E-commerce or E-payment technology before 2020. $covid_t$ captures the impact of COVID using the monthly \textit{Stringency Index}.

The interaction term $tech_i \cdot covid_t$ investigates whether the adoption of E-commerce or E-payment technology before 2020 mitigates the impact of COVID on trade outcomes. Finally, fixed-effects are included for firm and month.

## 2.1 Intensive Margin Analysis


```{r}

# India - intensive margin regressions of the model that measure if tech adoption mitigated covid impacts (Regressions at the firm-month level)
source("../India/06_regressions_tech_mitigation_covid_firm_month_level_IND.R", chdir = TRUE)


# Mexico - intensive margin regressions of the model that measure if tech adoption mitigated covid impacts (Regressions at the firm-month level)
source("../Mexico/06_regressions_tech_mitigation_covid_firm_month_level_MEX.R", chdir = TRUE)


# Indonesia - intensive margin regressions of the model that measure if tech adoption mitigated covid impacts (Regressions at the firm-month level)
source("../Indonesia/06_regressions_tech_mitigation_covid_firm_month_level_IDN.R", chdir = TRUE)


```


```{r, eval = T}

reg_firm_month_tech_covid_mitig_IND[[2]]

```



```{r, eval = T}

reg_firm_month_tech_covid_mitig_MEX[[2]]

```



```{r, eval = T}

reg_firm_month_tech_covid_mitig_IDN[[2]]

```