---
title: "Analysis of the COVID-19 Shock, Technology and Trade"
subtitle: "Quality of Panjiva Foreign Partners Data - India and Indonesia"
author: "Simón Caicedo"
date: \today
header-includes:
  \usepackage{float}
  \usepackage{placeins}
  \usepackage{rotating}
  \usepackage{graphicx}
  \usepackage{booktabs}
  \usepackage{caption}
  \usepackage{longtable}
  \usepackage{breqn}
  \usepackage{threeparttable}
output:
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning  = FALSE)
```


```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

# Set Working Directory ----
fileloc <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(fileloc)
rm(fileloc)

# Libraries to be used ----
library(tidyverse)
library(haven)
library(data.table)
library(dtplyr)
library(readxl)
library(arrow)
library(ggplot2)
library(kableExtra)
library(ggthemes)


# Read objects with information about Foreign Panjiva Quality Data
load("../../Data/India/processed_data/quality_foreign_data_IND.RData")     # India 
load("../../Data/Indonesia/processed_data/quality_foreign_data_IDN.RData") # Indonesia
load("../../Data/Mexico/processed_data/quality_foreign_data_MEX.RData")    # Mexico

```

# 1. India 

The following plot illustrates the proportion of Indian firms with non-missing foreign trade partners in all observations. This proportion is calculated for each year of available data in India (2016-2022). Notably, the lowest proportion values for both Exports and Imports datasets can be observed in 2016 and 2019.


```{r, eval = T, fig.width=9, fig.height=4}

exp_quality_IND %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>%
  summarize(total_firms = n(),
            n_distinct_firms = n_distinct(domestic_company_id),
            firms_complete = sum(prop_obs == 1, na.rm = TRUE),
            firms_incomplete = sum(prop_obs != 1, na.rm = TRUE),
            prop_complete = firms_complete /total_firms) %>% 
  select(Year = year, Exports = prop_complete) %>% 
  left_join(imp_quality_IND %>% 
              filter(foreign_firm_missing == 0) %>% 
              group_by(year) %>%
              summarize(total_firms = n(),
                        firms_complete = sum(prop_obs == 1, na.rm = TRUE),
                        prop_complete = firms_complete /total_firms) %>% 
              select(Year = year, Imports = prop_complete),
            by="Year") %>% 
  pivot_longer(cols = c(Exports, Imports), 
               names_to = "data", 
               values_to = "proportion") %>% 
  ggplot()+
  geom_col(aes(x = Year, y = proportion, fill = as.factor(Year)), alpha = 0.75)+
  facet_wrap(~data)+
  ggtitle("Proportion of Firms with Non-Missing Foreign Partners Data by Year", 
          subtitle = "India")+
  ylab("Proportion")+
  scale_fill_economist()+
  theme_minimal()+
  theme(legend.position  = "None", 
        plot.title = element_text(hjust = 0.5, face = "bold"), 
        plot.subtitle = element_text(hjust = 0.5, face = "italic"))+
  scale_x_continuous(n.breaks = 7)


```

Additionally, for each year, we calculate the total number of observations per firm and determine the count of observations with non-missing foreign partners. Subsequently, we compute by firm-year the proportion of observations with non-missing foreign partners. Tables 1 and 2 display the summary statistics (Mean, Min, quantile 5, quantile 25, Median, quantile 75 and Max) of this variable for the exports and imports datasets, respectively.


```{r, eval = T}

exp_quality_IND %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  # Summary Statistics of the Variable Measuring the Proportion of Observations by Firm-Year with Non-Missing Foreign Partner
  summarize(Mean = mean(prop_obs),
            Min = min(prop_obs), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_obs, 0.25), 
            Median = median(prop_obs), 
            p75 = quantile(prop_obs, 0.75), 
            Max = max(prop_obs)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Exports India - Summary Statistics of Proportion of Firm Observations with Non-Missing Foreign Partners", 
        booktabs = T, 
        linesep = "", 
        align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))



```




```{r, eval = T}

imp_quality_IND %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  summarize(Mean = mean(prop_obs),
            Min = min(prop_obs), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_obs, 0.25), 
            Median = median(prop_obs), 
            p75 = quantile(prop_obs, 0.75), 
            Max = max(prop_obs)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Imports India - Summary Statistics of Proportion of Firm Observations with Non-Missing Foreign Partners",
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))


```


As illustrated in Tables 1 and 2, the exports dataset shows an average proportion of non-missing foreign partner observations per firm across all years exceeding 0.8, with a median proportion of 1 for all years, except 2016. Meanwhile, the imports dataset presents an average proportion surpassing 0.94 for 2018, 2020, 2021, and 2022, along with a median proportion of 1 for these years.



On the other hand, to assess the importance of non-missing foreign partner observations in relation to a firm's total export or import volume for a specific year, we first calculate the annual total export or import volume for each firm. Following that, we compute by firm-year the proportion of the total volume attributable to observations with non-missing foreign partners. Summary statistics for this variable can be found in Tables 3 and 4 for the exports and imports datasets, respectively.


```{r, eval=T}

exp_quality_IND %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  summarize(Mean = mean(prop_trade_volume),
            Min = min(prop_trade_volume), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_trade_volume, 0.25), 
            Median = median(prop_trade_volume), 
            p75 = quantile(prop_trade_volume, 0.75), 
            Max = max(prop_trade_volume)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Exports India - Summary Statistics of Proportion of Firm Total Exports with Non-Missing Foreign Partners", 
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))



```



```{r, eval = T}

# Summary Statistics of the Variable Measuring the Proportion of Trade Volume by Firm-Year with Non-Missing Foreign Partner
imp_quality_IND %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  summarize(Mean = mean(prop_trade_volume),
            Min = min(prop_trade_volume), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_trade_volume, 0.25), 
            Median = median(prop_trade_volume), 
            p75 = quantile(prop_trade_volume, 0.75), 
            Max = max(prop_trade_volume)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Imports India - Summary Statistics of Proportion of Firm Total Imports with Non-Missing Foreign Partners",
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))


  
```


As shown in Tables 3 and 4, for the exports dataset, the average proportion of total trade volume attributed to non-missing foreign partner observations per firm across all years exceeds 0.79, with a median proportion of 1 for all years, except 2016. In the imports dataset, this average proportion surpasses 0.94 for 2018, 2020, 2021, and 2022, and the median proportion is 1 for these years as well.


# 2. Indonesia 

The datasets for Indonesia exhibit very few missing values concerning foreign partners. Across all years and in both exports and imports datasets, the proportion of Indonesian firms with non-missing foreign trade partners in all observations exceeds 0.96.


```{r, eval = T, fig.width=9, fig.height=5}

exp_quality_IDN %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>%
  summarize(total_firms = n(),
            firms_complete = sum(prop_obs == 1, na.rm = TRUE),
            prop_complete = firms_complete /total_firms) %>% 
  select(Year = year, Exports = prop_complete) %>% 
  left_join(imp_quality_IDN %>% 
              filter(foreign_firm_missing == 0) %>% 
              group_by(year) %>%
              summarize(total_firms = n(),
                        firms_complete = sum(prop_obs == 1, na.rm = TRUE),
                        prop_complete = firms_complete /total_firms) %>% 
              select(Year = year, Imports = prop_complete),
            by="Year") %>% 
  pivot_longer(cols = c(Exports, Imports), 
               names_to = "data", 
               values_to = "proportion") %>% 
  ggplot()+
  geom_col(aes(x = Year, y = proportion, fill = as.factor(Year)), alpha = 0.75)+
  facet_wrap(~data)+
  ggtitle("Proportion of Firms with Non-Missing Foreign Partners Data", 
          subtitle = "Indonesia")+
  ylab("Proportion")+
  scale_fill_economist()+
  theme_minimal()+
  theme(legend.position  = "None", 
        plot.title = element_text(hjust = 0.5, face = "bold"), 
        plot.subtitle = element_text(hjust = 0.5, face = "italic"))
  


```



```{r, eval = T}

exp_quality_IDN %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  # Summary Statistics of the Variable Measuring the Proportion of Observations by Firm-Year with Non-Missing Foreign Partner
  summarize(Mean = mean(prop_obs),
            Min = min(prop_obs), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_obs, 0.25), 
            Median = median(prop_obs), 
            p75 = quantile(prop_obs, 0.75), 
            Max = max(prop_obs)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Exports Indonesia - Summary Statistics of Proportion of Firm Observations with Non-Missing Foreign Partners", 
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))



```



```{r, eval = T}

exp_quality_IDN %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  summarize(Mean = mean(prop_trade_volume),
            Min = min(prop_trade_volume), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_trade_volume, 0.25), 
            Median = median(prop_trade_volume), 
            p75 = quantile(prop_trade_volume, 0.75), 
            Max = max(prop_trade_volume)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Exports Indonesia - Summary Statistics of Proportion of Firm Total Exports with Non-Missing Foreign Partners", 
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))



```



```{r, eval = T}

imp_quality_IDN %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  summarize(Mean = mean(prop_obs),
            Min = min(prop_obs), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_obs, 0.25), 
            Median = median(prop_obs), 
            p75 = quantile(prop_obs, 0.75), 
            Max = max(prop_obs)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Imports Indonesia - Summary Statistics of Proportion of Firm Observations with Non-Missing Foreign Partners",
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))




# Summary Statistics of the Variable Measuring the Proportion of Trade Volume by Firm-Year with Non-Missing Foreign Partner
imp_quality_IDN %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  summarize(Mean = mean(prop_trade_volume),
            Min = min(prop_trade_volume), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_trade_volume, 0.25), 
            Median = median(prop_trade_volume), 
            p75 = quantile(prop_trade_volume, 0.75), 
            Max = max(prop_trade_volume)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Imports Mexico - Summary Statistics of Proportion of Firm Total Imports with Non-Missing Foreign Partners",
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))


  
```

# 3. Mexico

The datasets for Mexico exhibit very few missing values concerning foreign partners. In all years, except for 2012-2014, the proportion of Mexican firms with non-missing foreign trade partners in both exports and imports datasets exceeds 0.75 for all observations.

```{r, eval = T, fig.width=9, fig.height=5}

exp_quality_MEX %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>%
  summarize(total_firms = n(),
            firms_complete = sum(prop_obs == 1, na.rm = TRUE),
            prop_complete = firms_complete /total_firms) %>% 
  select(Year = year, Exports = prop_complete) %>% 
  left_join(imp_quality_MEX %>% 
              filter(foreign_firm_missing == 0) %>% 
              group_by(year) %>%
              summarize(total_firms = n(),
                        firms_complete = sum(prop_obs == 1, na.rm = TRUE),
                        prop_complete = firms_complete /total_firms) %>% 
              select(Year = year, Imports = prop_complete),
            by="Year") %>% 
  pivot_longer(cols = c(Exports, Imports), 
               names_to = "data", 
               values_to = "proportion") %>% 
  ggplot()+
  geom_col(aes(x = as.factor(Year), y = proportion, fill = as.factor(Year)), alpha = 0.75)+
  facet_wrap(~data)+
  ggtitle("Proportion of Firms with Non-Missing Foreign Partners Data", 
          subtitle = "Mexico")+
  ylab("Proportion")+
  xlab("Year")+
  theme_minimal()+
  theme(legend.position  = "None", 
        plot.title = element_text(hjust = 0.5, face = "bold"), 
        plot.subtitle = element_text(hjust = 0.5, face = "italic"))+
  scale_fill_manual(values = c("#3E647D", "#7B92A8", "#82C0E9", "#2D6D66", "#BFA19C", "#008BBC", "#97B6B0", "#D7D29E", "#1A476F", "#90353B", "#9C8847", "#938DD2" 
))+
  scale_y_continuous(n.breaks= 10)


```



```{r, eval = T}

exp_quality_MEX %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  # Summary Statistics of the Variable Measuring the Proportion of Observations by Firm-Year with Non-Missing Foreign Partner
  summarize(Mean = mean(prop_obs),
            Min = min(prop_obs), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_obs, 0.25), 
            Median = median(prop_obs), 
            p75 = quantile(prop_obs, 0.75), 
            Max = max(prop_obs)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Exports Mexico - Summary Statistics of Proportion of Firm Observations with Non-Missing Foreign Partners", 
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))



```



```{r, eval = T}

exp_quality_MEX %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  summarize(Mean = mean(prop_trade_volume),
            Min = min(prop_trade_volume), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_trade_volume, 0.25), 
            Median = median(prop_trade_volume), 
            p75 = quantile(prop_trade_volume, 0.75), 
            Max = max(prop_trade_volume)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Exports Mexico - Summary Statistics of Proportion of Firm Total Exports with Non-Missing Foreign Partners", 
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))



```



```{r, eval = T}

imp_quality_MEX %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  summarize(Mean = mean(prop_obs),
            Min = min(prop_obs), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_obs, 0.25), 
            Median = median(prop_obs), 
            p75 = quantile(prop_obs, 0.75), 
            Max = max(prop_obs)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Imports Mexico - Summary Statistics of Proportion of Firm Observations with Non-Missing Foreign Partners",
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))




# Summary Statistics of the Variable Measuring the Proportion of Trade Volume by Firm-Year with Non-Missing Foreign Partner
imp_quality_MEX %>% 
  filter(foreign_firm_missing == 0) %>% 
  group_by(year) %>% 
  summarize(Mean = mean(prop_trade_volume),
            Min = min(prop_trade_volume), 
            p5 = quantile(prop_trade_volume, 0.05),
            p25 = quantile(prop_trade_volume, 0.25), 
            Median = median(prop_trade_volume), 
            p75 = quantile(prop_trade_volume, 0.75), 
            Max = max(prop_trade_volume)) %>% 
  # Round values 
  mutate(across(everything(), ~ round(., 3))) %>% 
  column_to_rownames("year") %>% 
  # Create Table
  kable(caption = "Panjiva Imports Mexico - Summary Statistics of Proportion of Firm Total Imports with Non-Missing Foreign Partners",
        booktabs = T, linesep = "", align = c("l",rep("c", 7))) %>% 
  kable_styling(latex_options = c("HOLD_position"))


  
```

