---
title: "Analysis of the COVID-19 Shock, Technology and Trade"
subtitle: "Summary Statistics of Variables Used in Regressions"
author: "Simón Caicedo"
date: \today
header-includes:
  \usepackage{float}
  \usepackage{placeins}
  \usepackage{rotating}
  \usepackage{graphicx}
  \usepackage{booktabs}
  \usepackage{caption}
  \usepackage{longtable}
  \usepackage{breqn}
  \usepackage{threeparttable}
output:
  pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning  = FALSE)


big_number_format<-function(x){format(x, big.mark = ",")}

```


```{r}

fileloc <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(fileloc)
rm(fileloc)

# Libraries to be used ----
source("../src/packages.R")
library(tibble)
library(ggpubr)

# Indonesia ----

# Builtwith Data 
tech_IDN <- read_parquet("../../Data/Indonesia/raw_data/Builtwith_no_drop_long_v2.parquet", 
                         col_select = c("New_ID_1", "tech")) %>% 
  rename(company_id = New_ID_1) %>% 
  filter(tech %in% c("pay_robust", "ecom_nod")) %>% 
  distinct(company_id)

# Load matched Aberdeen to Panjiva data 
aberdeen_IDN <- read_xlsx("../../Data/Indonesia/raw_data/matched_data_Indonesia.xlsx") 

# Correspondance 
IDN_Domestic_Ids_Corresp <- read_xlsx("../../Data/Indonesia/raw_data/IDN_Domestic_Ids_Corresp_update.xlsx")

aberdeen_IDN <-IDN_Domestic_Ids_Corresp  %>% 
  select(prev_our_domestic_id, new_our_domestic_id ) %>% 
  distinct() %>% 
  filter(prev_our_domestic_id  %in% aberdeen_IDN$our_domestic_id) %>% 
  left_join(aberdeen_IDN,  by = c("prev_our_domestic_id" = "our_domestic_id")) %>% 
  rename(company_id = new_our_domestic_id) %>% 
  distinct(company_id)


# Panjiva Imports Data (Firm-Month-HS6)
imports_IDN <-read_csv("../../Data/Indonesia/processed_data/import_summary_by_firm_month_HS_code.csv") %>% 
  select(company_id, date, date_character,hs6,log_import, import, import_dummy, n_countries_import)%>% 
  mutate(hs6  = str_pad(hs6 , 6, "left", "0"), 
         year = year(date)) %>% 
  mutate(matched_builtwith = company_id %in% tech_IDN$company_id, 
         matched_aberdeen = company_id %in% aberdeen_IDN$company_id, 
         matched_both = as.logical(matched_builtwith*matched_aberdeen))

# Panjiva Exports Data (Firm-Month-HS6)
exports_IDN <-read_csv("../../Data/Indonesia/processed_data/export_summary_by_firm_month_HS_code.csv") %>% 
  select(company_id, date, date_character,hs6, log_export, export, export_dummy, n_countries_export)%>% 
  mutate(hs6  = str_pad(hs6 , 6, "left", "0"), 
         year = year(date)) %>% 
  mutate(matched_builtwith = company_id %in% tech_IDN$company_id, 
         matched_aberdeen = company_id %in% aberdeen_IDN$company_id, 
         matched_both = as.logical(matched_builtwith*matched_aberdeen))


# India ----

# Builtwith India 
tech_IND   <- read_parquet("../../Data/India/raw_data/Builtwith_no_drop_long_v2.parquet", 
                            col_select = c("our_ID", "tech")) %>% 
  # For the moment, we are only going to analyze e-payment/e-commerce technologies
  filter(tech %in% c("payrobust_nod", "ecom_nod")) %>% 
  rename(company_id = our_ID) %>% 
  distinct(company_id)

# Firms matched to Aberdeen 
aberdeen_IND <- read_csv("../../Data/India/raw_data/matched_Aberdeen_to_Panjiva_data_India_v2.csv") %>%
  rename(company_id = our_ID) %>% 
  distinct(company_id)


# Panjiva Imports Data 
imports_IND <-fread("../../Data/India/processed_data/import_summaries_by_firm_month_HS_code_complete.csv") %>% 
  select(company_id = domestic_company_id, year, month, date, date_character,hs6, import, log_import) %>%
  # filter to analysis period
  filter(date >= ymd("2018-07-01"),
         date < ymd("2022-01-01")) %>% 
  mutate(hs6  = str_pad(as.character(hs6), 6, "left", "0"), 
         matched_builtwith = company_id %in% tech_IND$company_id, 
         matched_aberdeen = company_id %in% aberdeen_IND$company_id, 
         matched_both = as.logical(matched_aberdeen*matched_builtwith)) %>% 
  as.data.frame()


# Panjiva Exports Data 
exports_IND <-fread("../../Data/India/processed_data/export_summaries_by_firm_month_HS_code_complete.csv") %>% 
  select(company_id = domestic_company_id, year, month, date, date_character,hs6, export, log_export) %>% 
  # filter to analysis period
  filter(date >= ymd("2018-07-01"),
         date < ymd("2022-01-01"))%>% 
  mutate(hs6  = str_pad(as.character(hs6) , 6, "left", "0"), 
         matched_builtwith = company_id %in% tech_IND$company_id, 
         matched_aberdeen = company_id %in% aberdeen_IND$company_id,
         matched_both = as.logical(matched_aberdeen*matched_builtwith)) %>% 
  as.data.frame()

rm(IDN_Domestic_Ids_Corresp)


```


# Matching Description

The tables in this section display the proportion of transactions or firms per country-year represented by the matched Panjiva-Aberdeen-BuiltWith samples. Please note that these percentages pertain only to the matched Panjiva-Aberdeen-BuiltWith dataset and not to the regressions sample. The regressions sample has other filters, for example, excludes firms that do not fall within the analyzed SIC groups (Wholesale/Retail, Manufacturing, Agriculture, Construction and Mining, Services, Finance, Insurance and Real Estate, and Transport and Utilities) and those with total imports/exports of less than 1000 USD across all years. 

## Total Exports and Imports Matching Rates by Year

```{r}

table_IDN<-imports_IDN %>% 
  select(year, import, matched_builtwith, matched_aberdeen, matched_both) %>% 
  mutate(Data = "Panjiva Imports") %>% 
  group_by(year) %>% 
  mutate(total_imports = sum(import, na.rm = T)) %>%
  ungroup() %>% 
  group_by(year, matched_builtwith) %>% 
  mutate(tot_imp_match_builtwith = sum(import, na.rm = T), 
         share_match_builtwith = (tot_imp_match_builtwith/total_imports)*100) %>%
  ungroup() %>%
  group_by(year, matched_aberdeen) %>% 
  mutate(tot_imp_match_aberdeen = sum(import, na.rm = T), 
         share_match_aberdeen = (tot_imp_match_aberdeen/total_imports)*100) %>% 
  ungroup() %>% 
  group_by(year, matched_both) %>% 
  mutate(tot_imp_match_both = sum(import, na.rm=T), 
         share_match_both = (tot_imp_match_both/total_imports)*100) %>% 
  ungroup() %>% 
  filter(matched_builtwith == T, 
         matched_aberdeen  == T, 
         matched_both == T) %>% 
  distinct(year, .keep_all = T) %>% 
  select(Data,
         Year = year,
         `Total Value` = total_imports,
         `% Matched Aberdeen` = share_match_aberdeen,
         `% Matched BuiltWith` = share_match_builtwith, 
         `% Matched Both` = share_match_both
         ) %>% 
  bind_rows(
      exports_IDN %>% 
      select(year, export, matched_builtwith, matched_aberdeen, matched_both) %>% 
      mutate(Data = "Panjiva Exports") %>% 
      group_by(year) %>% 
      mutate(total_exports = sum(export, na.rm = T)) %>% 
      ungroup() %>% 
      group_by(year, matched_builtwith) %>% 
      mutate(tot_exp_match_builtwith = sum(export, na.rm = T), 
             share_match_builtwith = (tot_exp_match_builtwith/total_exports)*100) %>%
      ungroup() %>%
      group_by(year, matched_aberdeen) %>% 
      mutate(tot_exp_match_aberdeen = sum(export, na.rm = T), 
             share_match_aberdeen = (tot_exp_match_aberdeen/total_exports)*100) %>% 
      ungroup() %>% 
      group_by(year, matched_both) %>% 
      mutate(tot_exp_match_both = sum(export, na.rm = T), 
             share_match_both = (tot_exp_match_both/total_exports)*100) %>% 
      ungroup() %>% 
      filter(matched_builtwith == T, 
             matched_aberdeen  == T, 
             matched_both == T) %>% 
      distinct(year, .keep_all = T) %>% 
      select(Data,
             Year = year,
             `Total Value` = total_exports,
             `% Matched Aberdeen` = share_match_aberdeen,
             `% Matched BuiltWith` = share_match_builtwith, 
             `% Matched Both` = share_match_both
             )
  ) %>% 
  mutate(across(where(is.numeric), round, 2), 
         across(c(`Total Value`), big_number_format)) %>% 
  mutate(`Total Value` = paste0("$", `Total Value`))

table_IND<-imports_IND %>% 
  select(year, import, matched_builtwith, matched_aberdeen, matched_both) %>% 
  mutate(Data = "Panjiva Imports") %>% 
  group_by(year) %>% 
  mutate(total_imports = sum(import, na.rm = T)) %>%
  ungroup() %>% 
  group_by(year, matched_builtwith) %>% 
  mutate(tot_imp_match_builtwith = sum(import, na.rm = T), 
         share_match_builtwith = (tot_imp_match_builtwith/total_imports)*100) %>%
  ungroup() %>%
  group_by(year, matched_aberdeen) %>% 
  mutate(tot_imp_match_aberdeen = sum(import, na.rm = T), 
         share_match_aberdeen = (tot_imp_match_aberdeen/total_imports)*100) %>% 
  ungroup() %>% 
  group_by(year, matched_both) %>% 
  mutate(tot_imp_match_both = sum(import, na.rm=T), 
         share_match_both = (tot_imp_match_both/total_imports)*100) %>% 
  ungroup() %>% 
  filter(matched_builtwith == T, 
         matched_aberdeen  == T, 
         matched_both == T) %>% 
  distinct(year, .keep_all = T) %>% 
  select(Data,
         Year = year,
         `Total Value` = total_imports,
         `% Matched Aberdeen` = share_match_aberdeen,
         `% Matched BuiltWith` = share_match_builtwith, 
         `% Matched Both` = share_match_both
  ) %>% 
  bind_rows(
    exports_IND %>% 
      select(year, export, matched_builtwith, matched_aberdeen, matched_both) %>% 
      mutate(Data = "Panjiva Exports") %>% 
      group_by(year) %>% 
      mutate(total_exports = sum(export, na.rm = T)) %>% 
      ungroup() %>% 
      group_by(year, matched_builtwith) %>% 
      mutate(tot_exp_match_builtwith = sum(export, na.rm = T), 
             share_match_builtwith = (tot_exp_match_builtwith/total_exports)*100) %>%
      ungroup() %>%
      group_by(year, matched_aberdeen) %>% 
      mutate(tot_exp_match_aberdeen = sum(export, na.rm = T), 
             share_match_aberdeen = (tot_exp_match_aberdeen/total_exports)*100) %>% 
      ungroup() %>% 
      group_by(year, matched_both) %>% 
      mutate(tot_exp_match_both = sum(export, na.rm = T), 
             share_match_both = (tot_exp_match_both/total_exports)*100) %>% 
      ungroup() %>% 
      filter(matched_builtwith == T, 
             matched_aberdeen  == T, 
             matched_both == T) %>% 
      distinct(year, .keep_all = T) %>% 
      select(Data,
             Year = year,
             `Total Value` = total_exports,
             `% Matched Aberdeen` = share_match_aberdeen,
             `% Matched BuiltWith` = share_match_builtwith, 
             `% Matched Both` = share_match_both
      )
  ) %>% 
  mutate(across(where(is.numeric), round, 2), 
         across(c(`Total Value`), big_number_format)) %>% 
  mutate(`Total Value` = paste0("$", `Total Value`))

```


```{r, eval=TRUE}

kable(table_IDN %>% select(-Data), 
    caption = "Indonesia - Panjiva total imports and total exports matching rates to BuiltWith and Aberdeen datasets by year", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Panjiva Imports", 1, 3) %>%
  pack_rows("Panjiva Exports", 4, 6) %>% 
  add_footnote(c("Data available for imports from February 2019 to June 2021",
                 "Data available for exports from February 2019 to September 2021"))



```


```{r, eval=TRUE}

kbl(table_IND %>% select(-Data), 
    caption = "India - Panjiva total imports and total exports matching rates to BuiltWith and Aberdeen datasets by year", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Panjiva Imports", 1, 4) %>%
  pack_rows("Panjiva Exports", 5, 8)%>% 
  add_footnote(c("Data from July 2018 onwards is included."))


```



## Firms Matching Rates by Year

```{r}

table_IDN<-imports_IDN %>% 
  select(company_id, year, matched_builtwith, matched_aberdeen, matched_both) %>% 
  distinct(company_id, year, .keep_all = T) %>% 
  mutate(Data = "Panjiva Imports") %>% 
  group_by(year) %>% 
  mutate(n_firms = n()) %>%
  ungroup() %>% 
  group_by(year, matched_builtwith) %>% 
  mutate(n_match_builtwith = sum(matched_builtwith), 
         share_match_builtwith = (n_match_builtwith/n_firms)*100) %>%
  ungroup() %>%
  group_by(year, matched_aberdeen) %>% 
  mutate(n_match_aberdeen = sum(matched_aberdeen), 
         share_match_aberdeen = (n_match_aberdeen/n_firms)*100) %>% 
  ungroup() %>% 
  group_by(year, matched_both) %>% 
  mutate(n_match_both = sum(matched_both), 
         share_match_both = (n_match_both/n_firms)*100) %>% 
  ungroup() %>% 
  filter(share_match_builtwith != 0, 
         share_match_aberdeen != 0, 
         share_match_both != 0) %>% 
  distinct(n_firms, share_match_builtwith, share_match_aberdeen, share_match_both, .keep_all = T) %>% 
  select(Data,
         Year = year,
         `Number Firms` = n_firms,
         `% Matched Aberdeen` = share_match_aberdeen,
         `% Matched BuiltWith` = share_match_builtwith, 
         `% Matched Both` = share_match_both
         ) %>% 
  bind_rows(
      exports_IDN %>% 
      select(company_id, year, matched_builtwith, matched_aberdeen, matched_both) %>% 
      distinct(company_id, year, .keep_all = T) %>% 
      mutate(Data = "Panjiva Exports") %>% 
      group_by(year) %>% 
      mutate(n_firms = n()) %>% 
      group_by(year, matched_builtwith) %>% 
      mutate(n_match_builtwith = sum(matched_builtwith), 
             share_match_builtwith = (n_match_builtwith/n_firms)*100) %>%
      ungroup() %>%
      group_by(year, matched_aberdeen) %>% 
      mutate(n_match_aberdeen = sum(matched_aberdeen), 
             share_match_aberdeen = (n_match_aberdeen/n_firms)*100) %>% 
      ungroup() %>% 
      group_by(year, matched_both) %>% 
      mutate(n_match_both = sum(matched_both), 
             share_match_both = (n_match_both/n_firms)*100) %>% 
      ungroup() %>% 
      filter(share_match_builtwith != 0, 
             share_match_aberdeen != 0, 
             share_match_both != 0) %>% 
      distinct(n_firms, share_match_builtwith, share_match_aberdeen, share_match_both, .keep_all = T) %>% 
      select(Data,
             Year = year,
             `Number Firms` = n_firms,
             `% Matched Aberdeen` = share_match_aberdeen,
             `% Matched BuiltWith` = share_match_builtwith, 
             `% Matched Both` = share_match_both
             )
  ) %>% 
  mutate(across(where(is.numeric), round, 2), 
         across(`Number Firms`, big_number_format))



table_IND<-imports_IND %>% 
  select(company_id, year, matched_builtwith, matched_aberdeen, matched_both) %>% 
  distinct(company_id, year, .keep_all = T) %>% 
  mutate(Data = "Panjiva Imports") %>% 
  group_by(year) %>% 
  mutate(n_firms = n()) %>% 
  ungroup() %>% 
  group_by(year, matched_builtwith) %>% 
  mutate(n_match_builtwith = sum(matched_builtwith), 
         share_match_builtwith = (n_match_builtwith/n_firms)*100) %>%
  ungroup() %>%
  group_by(year, matched_aberdeen) %>% 
  mutate(n_match_aberdeen = sum(matched_aberdeen), 
         share_match_aberdeen = (n_match_aberdeen/n_firms)*100) %>% 
  ungroup() %>% 
  group_by(year, matched_both) %>% 
  mutate(n_match_both = sum(matched_both), 
         share_match_both = (n_match_both/n_firms)*100) %>% 
  ungroup() %>% 
  filter(share_match_builtwith != 0, 
         share_match_aberdeen != 0, 
         share_match_both != 0) %>% 
  distinct(n_firms, share_match_builtwith, share_match_aberdeen, share_match_both, .keep_all = T) %>% 
  select(Data,
         Year = year,
         `Number Firms` = n_firms,
         `% Matched Aberdeen` = share_match_aberdeen,
         `% Matched BuiltWith` = share_match_builtwith, 
         `% Matched Both` = share_match_both) %>% 
  bind_rows(
      exports_IND %>% 
      select(company_id, year, matched_builtwith, matched_aberdeen, matched_both) %>% 
      distinct(company_id, year, .keep_all = T) %>% 
      mutate(Data = "Panjiva Exports") %>% 
      group_by(year) %>% 
      mutate(n_firms = n()) %>% 
      group_by(year, matched_builtwith) %>% 
      mutate(n_match_builtwith = sum(matched_builtwith), 
             share_match_builtwith = (n_match_builtwith/n_firms)*100) %>%
      ungroup() %>%
      group_by(year, matched_aberdeen) %>% 
      mutate(n_match_aberdeen = sum(matched_aberdeen), 
             share_match_aberdeen = (n_match_aberdeen/n_firms)*100) %>% 
      ungroup() %>% 
      group_by(year, matched_both) %>% 
      mutate(n_match_both = sum(matched_both), 
             share_match_both = (n_match_both/n_firms)*100) %>% 
      ungroup() %>% 
      distinct(n_firms, share_match_builtwith, share_match_aberdeen, share_match_both, .keep_all = T) %>% 
      filter(share_match_builtwith != 0, 
             share_match_aberdeen != 0, 
             share_match_both!= 0) %>% 
      select(Data,
             Year = year,
             `Number Firms` = n_firms,
             `% Matched Aberdeen` = share_match_aberdeen,
             `% Matched BuiltWith` = share_match_builtwith, 
             `% Matched Both` = share_match_both)
  ) %>% 
  mutate(across(where(is.numeric), round, 2), 
         across(`Number Firms`, big_number_format))


```


```{r, eval=TRUE}

kable(table_IDN %>% select(-Data), 
    caption = "Indonesia - Panjiva firms matching rates to BuiltWith and Aberdeen datasets by year", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Panjiva Imports", 1, 3) %>%
  pack_rows("Panjiva Exports", 4, 6)


```



```{r, eval=TRUE}

kbl(table_IND %>% select(-Data), 
    caption = "India - Panjiva firms matching rates to BuiltWith and Aberdeen datasets by year", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Panjiva Imports", 1, 4) %>%
  pack_rows("Panjiva Exports", 5, 8)


```

## Transactions Matching Rates by Year

```{r, eval = TRUE}

table_IDN<-imports_IDN %>% 
  select(company_id, year, matched_builtwith, matched_aberdeen, matched_both) %>% 
  mutate(Data = "Panjiva Imports") %>% 
  group_by(year) %>% 
  mutate(n_transactions = n()) %>% 
  ungroup() %>% 
  group_by(year, matched_builtwith) %>% 
  mutate(n_match_builtwith = sum(matched_builtwith), 
         share_match_builtwith = (n_match_builtwith/n_transactions)*100) %>%
  ungroup() %>% 
  group_by(year, matched_aberdeen) %>% 
  mutate(n_match_aberdeen = sum(matched_aberdeen), 
         share_match_aberdeen = (n_match_aberdeen/n_transactions)*100) %>%
  ungroup() %>% 
  group_by(year, matched_both) %>% 
  mutate(n_match_both = sum(matched_both), 
         share_match_both = (n_match_both/n_transactions)*100) %>%
  ungroup() %>% 
  distinct(n_transactions, share_match_builtwith, share_match_aberdeen, share_match_both, .keep_all = T) %>% 
  filter(share_match_builtwith != 0, 
         share_match_aberdeen != 0, 
         share_match_both!=0) %>% 
  select(Data,
         Year = year,
         `Number Transactions` = n_transactions,
         `% Matched Aberdeen` = share_match_aberdeen,
         `% Matched BuiltWith` = share_match_builtwith,
         `% Matched Both` = share_match_both
         ) %>%  
  bind_rows(exports_IDN %>% 
              select(company_id, year, matched_builtwith, matched_aberdeen, matched_both) %>%
              mutate(Data = "Panjiva Exports") %>% 
              group_by(year) %>% 
              mutate(n_transactions = n()) %>% 
              ungroup() %>% 
              group_by(year, matched_builtwith) %>% 
              mutate(n_match_builtwith = sum(matched_builtwith), 
                     share_match_builtwith = (n_match_builtwith/n_transactions)*100) %>%
              ungroup() %>% 
              group_by(year, matched_aberdeen) %>% 
              mutate(n_match_aberdeen = sum(matched_aberdeen), 
                     share_match_aberdeen = (n_match_aberdeen/n_transactions)*100) %>%
              ungroup() %>% 
              group_by(year, matched_both) %>% 
              mutate(n_match_both = sum(matched_both), 
                     share_match_both = (n_match_both/n_transactions)*100) %>%
              ungroup() %>% 
              distinct(n_transactions, share_match_builtwith, share_match_aberdeen, share_match_both, .keep_all = T) %>% 
              filter(share_match_builtwith != 0,
                     share_match_aberdeen != 0,
                     share_match_both != 0) %>% 
              select(Data,
                     Year = year,
                     `Number Transactions` = n_transactions,
                     `% Matched Aberdeen` = share_match_aberdeen,
                     `% Matched BuiltWith` = share_match_builtwith, 
                     `% Matched Both` = share_match_both)
            ) %>% 
  mutate(across(where(is.numeric), round, 2), 
         across(`Number Transactions`, big_number_format))
  
  
table_IND <- imports_IND %>% 
  select(company_id, year, matched_builtwith, matched_aberdeen, matched_both) %>% 
  mutate(Data = "Panjiva Imports") %>% 
  group_by(year) %>% 
  mutate(n_transactions = n()) %>% 
  ungroup() %>% 
  group_by(year, matched_builtwith) %>% 
  mutate(n_match_builtwith = sum(matched_builtwith), 
         share_match_builtwith = (n_match_builtwith/n_transactions)*100) %>%
  ungroup() %>% 
  group_by(year, matched_aberdeen) %>% 
  mutate(n_match_aberdeen = sum(matched_aberdeen), 
         share_match_aberdeen = (n_match_aberdeen/n_transactions)*100) %>%
  ungroup() %>% 
  group_by(year, matched_both) %>% 
  mutate(n_match_both = sum(matched_both), 
         share_match_both = (n_match_both/n_transactions)*100) %>%
  ungroup() %>% 
  distinct(n_transactions, share_match_builtwith, share_match_aberdeen, share_match_both, .keep_all = T) %>% 
  filter(share_match_builtwith != 0, 
         share_match_aberdeen != 0, 
         share_match_both!=0) %>% 
  select(Data,
         Year = year,
         `Number Transactions` = n_transactions,
         `% Matched Aberdeen` = share_match_aberdeen,
         `% Matched BuiltWith` = share_match_builtwith,
         `% Matched Both` = share_match_both
         ) %>% 
  bind_rows(exports_IND %>% 
              select(company_id, year, matched_builtwith, matched_aberdeen, matched_both) %>% 
              mutate(Data = "Panjiva Exports") %>% 
              group_by(year) %>% 
              mutate(n_transactions = n()) %>% 
              ungroup() %>% 
              group_by(year, matched_builtwith) %>% 
              mutate(n_match_builtwith = sum(matched_builtwith), 
                     share_match_builtwith = (n_match_builtwith/n_transactions)*100) %>%
              ungroup() %>% 
              group_by(year, matched_aberdeen) %>% 
              mutate(n_match_aberdeen = sum(matched_aberdeen), 
                     share_match_aberdeen = (n_match_aberdeen/n_transactions)*100) %>%
              ungroup() %>% 
              group_by(year, matched_both) %>% 
              mutate(n_match_both = sum(matched_both), 
                     share_match_both = (n_match_both/n_transactions)*100) %>%
              ungroup() %>% 
              distinct(n_transactions, share_match_builtwith, share_match_aberdeen, share_match_both, .keep_all = T) %>% 
              filter(share_match_builtwith != 0,
                     share_match_aberdeen != 0,
                     share_match_both != 0
                     
                     ) %>% 
              select(Data,
                     Year = year, 
                     `Number Transactions` = n_transactions,
                     `% Matched Aberdeen` = share_match_aberdeen,
                     `% Matched BuiltWith` = share_match_builtwith, 
                     `% Matched Both` = share_match_both
                     )) %>% 
  mutate(across(where(is.numeric), round, 2), 
         across(`Number Transactions`, big_number_format))

```



```{r, eval=TRUE}

kbl(table_IDN %>% select(-Data), 
    caption = "Indonesia - Panjiva transactions at the Firm-Month-HS6 level matching rates to BuiltWith and Aberdeen datasets by year", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Panjiva Imports", 1, 3) %>%
  pack_rows("Panjiva Exports", 4, 6)


```



```{r, eval=TRUE}

kbl(table_IND %>% select(-Data), 
    caption = "India - Panjiva transactions at the Firm-Month-HS6 level matching rates to BuiltWith and Aberdeen datasets by year", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Panjiva Imports", 1, 4) %>%
  pack_rows("Panjiva Exports", 5, 8)


```


```{r}

rm(list = ls())
big_number_format<-function(x){format(x, big.mark = ",")}


```

# Regression Samples for Intensive Margin 

## Regression Sample Summary Statistics: Does Tech Adoption Affect Trade Outcomes?

For the matched Panjiva-BuiltWith-Aberdeen dataset, we apply the following additional filters to obtain our regression sample for the model that assesses the impact of tech adoption on trade outcomes:

- Keep firms that belong to any of the analyzed SIC groups (Wholesale/Retail, Manufacturing, Agriculture, Construction and Mining, Services, Finance, Insurance and Real Estate, and Transport and Utilities)

- Drop firms that adopted the E-payment/E-commerce technology before the period of analysis. 

- Keep only firms that had website before and after period of analysis (This can be seen in the BuiltWith dataset).  


```{r, eval=T}

pay_ecom_import_data_IDN<-fread("../../Data/Indonesia/processed_data/imports_product_model_IDN.csv")
pay_ecom_export_data_IDN<-fread("../../Data/Indonesia/processed_data/exports_product_model_IDN.csv")

pay_ecom_import_data_IND<-fread("../../Data/India/processed_data/imports_product_model_IND.csv")
pay_ecom_export_data_IND<-fread("../../Data/India/processed_data/exports_product_model_IND.csv")

```



```{r, eval=T}

dep_vars<-
  # Indonesia
  pay_ecom_export_data_IDN %>% 
  as.data.frame() %>% 
  mutate(export = exp(log_export)) %>% 
  select(export) %>% 
  summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd)) %>% 
    bind_rows(pay_ecom_import_data_IDN %>% 
                as.data.frame() %>% 
                mutate(import = exp(log_import)) %>% 
                select(import) %>% 
                summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, 
                                   Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd))
              )%>% 
    mutate(across(where(is.numeric), round, 2), 
           across(where(is.numeric), big_number_format), 
           across(everything(), ~paste0("$", .))) %>% 
  # India
    bind_rows(pay_ecom_export_data_IND %>% 
      as.data.frame() %>% 
      mutate(export = exp(log_export)) %>% 
      select(export) %>% 
      summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd)) %>% 
      bind_rows(pay_ecom_import_data_IND %>% 
                  as.data.frame() %>% 
                  mutate(import = exp(log_import)) %>% 
                  select(import) %>% 
                  summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, 
                                     Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd))
                )%>% 
      mutate(across(where(is.numeric), round, 2), 
             across(where(is.numeric), big_number_format), 
             across(everything(), ~paste0("$", .))) 
    )
  

rownames(dep_vars)<-c("Exports", "Imports", "Exports ", "Imports ")

kbl(dep_vars, 
    caption = "Descriptive Statistics of Value of Imports and Exports - Regression Sample", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Indonesia", 1, 2) %>%
  pack_rows("India", 3, 4)

```


```{r, eval = T}


prods_tech<-
  # Indonesia Exports
  pay_ecom_export_data_IDN %>% 
  as.data.frame() %>% 
  select(tech = pay_or_ecomnod_t_2, Ebay_tradable, China_E_commerce, cons_BEC, durable_BEC) %>% 
  na.omit() %>% 
  summarize_all(list(Mean = mean)) %>% 
  pivot_longer(cols = everything(), 
               names_to = c("variable", "statistic"),
               names_pattern = "([A-Za-z_]+)_(Mean)") %>% 
  select(-statistic) %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  pivot_wider(names_from = variable, 
              values_from = value) %>% 
  bind_rows(
    # Indonesia Imports
    pay_ecom_import_data_IDN %>% 
    as.data.frame() %>% 
    select(tech = pay_or_ecomnod_t_2, Ebay_tradable, China_E_commerce, cons_BEC, durable_BEC) %>% 
    na.omit() %>% 
    summarize_all(list(Mean = mean)) %>% 
    pivot_longer(cols = everything(), 
                 names_to = c("variable", "statistic"),
                 names_pattern = "([A-Za-z_]+)_(Mean)") %>% 
    select(-statistic) %>% 
    mutate(across(where(is.numeric), round, 3)) %>% 
    pivot_wider(names_from = variable, 
                values_from = value)
    ) %>% 
  bind_rows(
    # India Exports
    pay_ecom_export_data_IND %>% 
    as.data.frame() %>% 
    select(tech = pay_or_ecomnod_t_2, Ebay_tradable, China_E_commerce, cons_BEC, durable_BEC) %>% 
    na.omit() %>% 
    summarize_all(list(Mean = mean)) %>% 
    pivot_longer(cols = everything(), 
                 names_to = c("variable", "statistic"),
                 names_pattern = "([A-Za-z_]+)_(Mean)") %>% 
    select(-statistic) %>% 
    mutate(across(where(is.numeric), round, 3)) %>% 
    pivot_wider(names_from = variable, 
                values_from = value) %>% 
    bind_rows(
      # India Imports
      pay_ecom_import_data_IND %>% 
      as.data.frame() %>% 
      select(tech = pay_or_ecomnod_t_2, Ebay_tradable, China_E_commerce, cons_BEC, durable_BEC) %>% 
      na.omit() %>% 
      summarize_all(list(Mean = mean)) %>% 
      pivot_longer(cols = everything(), 
                   names_to = c("variable", "statistic"),
                   names_pattern = "([A-Za-z_]+)_(Mean)") %>% 
      select(-statistic) %>% 
      mutate(across(where(is.numeric), round, 3)) %>% 
      pivot_wider(names_from = variable, 
                  values_from = value)
      )
      
  )

```


```{r, eval = T}

prods_tech<-as.data.frame(prods_tech)
rownames(prods_tech)<-c("Exports", "Imports", "Exports ", "Imports ")
colnames(prods_tech)<-c("E-payment/E-commerce", "e-Bay tradable", "China E-commerce", "Consumable", "Durable")

kbl(prods_tech, 
    caption = "Proportion of Observations with Dummy Variables Equal to 1 for E-payment/E-commerce, e-Bay Tradable, China E-commerce, Consumable, and Durable Product Categories - Regression Sample", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Indonesia", 1, 2) %>%
  pack_rows("India", 3, 4)


```

```{r, eval = T}

# It would also be useful to know how many exporting firms or importing firms are part of the sample.

n_firms<-
  # Indonesia Exports
  pay_ecom_export_data_IDN %>% 
  as.data.frame() %>% 
  distinct(company_id) %>% 
  summarize(`Exporting Firms` = n()) %>% 
  # Indonesia Imports 
  bind_cols(
   pay_ecom_import_data_IDN %>% 
    as.data.frame() %>% 
    distinct(company_id) %>% 
    summarize(`Importing Firms` = n()) 
  ) %>% 
  # India Exports
  bind_cols(pay_ecom_export_data_IND %>% 
    as.data.frame() %>% 
    distinct(company_id) %>% 
    summarize(`Exporting Fimrs` = n())
    ) %>% 
  # India Imports
   bind_cols(pay_ecom_import_data_IND %>% 
    as.data.frame() %>% 
    distinct(company_id) %>% 
    summarize(`Importing Fimrs` = n())
  ) %>% 
  mutate(across(everything(), big_number_format))
  
  


kbl(n_firms, 
    caption = "Number of Importing and Exporting Firms - Regression Sample", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  add_header_above(c("Indonesia" = 2, "India" = 2))

```


## Regression Sample: Does Existing Tech Use Mitigate COVID Impacts?


For the matched Panjiva-BuiltWith-Aberdeen dataset, we apply the following additional filters to obtain our regression sample for the model that assesses if tech adoption mitigates COVID impacts:

- Keep firms that belong to any of the analyzed SIC groups (Wholesale/Retail, Manufacturing, Agriculture, Construction and Mining, Services, Finance, Insurance and Real Estate, and Transport and Utilities)

- Keep only firms that had website before and after period of analysis.  

```{r}

rm(list = ls())
big_number_format<-function(x){format(x, big.mark = ",")}



```



```{r, eval=T}


import_mitig_data_IDN<-fread("../../Data/Indonesia/processed_data/imports_tech_mitigation_model_IDN.csv") %>% 
  mutate(month_mean_stringency_index = replace_na(month_mean_stringency_index, 0)) %>% 
  as.data.frame()
  
export_mitig_data_IDN<-fread("../../Data/Indonesia/processed_data/exports_tech_mitigation_model_IDN.csv") %>% 
  mutate(month_mean_stringency_index = replace_na(month_mean_stringency_index, 0))%>% 
  as.data.frame()

import_mitig_data_IND<-fread("../../Data/India/processed_data/imports_tech_mitigation_model_IND.csv") %>% 
  mutate(month_mean_stringency_index = replace_na(month_mean_stringency_index, 0))%>% 
  as.data.frame()

export_mitig_data_IND<-fread("../../Data/India/processed_data/exports_tech_mitigation_model_IND.csv") %>% 
  mutate(month_mean_stringency_index = replace_na(month_mean_stringency_index, 0))%>% 
  as.data.frame()

```



```{r, eval=T}

dep_vars<-
  # Indonesia
  export_mitig_data_IDN %>% 
  as.data.frame() %>% 
  mutate(export = exp(log_export)) %>% 
  select(export) %>% 
  summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd)) %>% 
    bind_rows(import_mitig_data_IDN %>% 
                as.data.frame() %>% 
                mutate(import = exp(log_import)) %>% 
                select(import) %>% 
                summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, 
                                   Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd))
              )%>% 
    mutate(across(where(is.numeric), round, 2), 
           across(where(is.numeric), big_number_format), 
           across(everything(), ~paste0("$", .))) %>% 
  # India
    bind_rows(export_mitig_data_IND %>% 
      as.data.frame() %>% 
      mutate(export = exp(log_export)) %>% 
      select(export) %>% 
      summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd)) %>% 
      bind_rows(import_mitig_data_IND %>% 
                  as.data.frame() %>% 
                  mutate(import = exp(log_import)) %>% 
                  select(import) %>% 
                  summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, 
                                     Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd))
                )%>% 
      mutate(across(where(is.numeric), round, 2), 
             across(where(is.numeric), big_number_format), 
             across(everything(), ~paste0("$", .))) 
    )
  

rownames(dep_vars)<-c("Exports", "Imports", "Exports ", "Imports ")

kbl(dep_vars, 
    caption = "Descriptive Statistics of Value of Imports and Exports", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Indonesia", 1, 2) %>%
  pack_rows("India", 3, 4)

```



```{r, eval = T}


prods_tech<-
  # Indonesia Exports
  export_mitig_data_IDN %>% 
  as.data.frame() %>% 
  select(tech = adopted_pay_or_ecom_before_2019, Ebay_tradable, China_E_commerce, cons_BEC, durable_BEC) %>% 
  na.omit() %>% 
  summarize_all(list(Mean = mean)) %>% 
  pivot_longer(cols = everything(), 
               names_to = c("variable", "statistic"),
               names_pattern = "([A-Za-z_]+)_(Mean)") %>% 
  select(-statistic) %>% 
  mutate(across(where(is.numeric), round, 3)) %>% 
  pivot_wider(names_from = variable, 
              values_from = value) %>% 
  bind_rows(
    # Indonesia Imports
    import_mitig_data_IDN %>% 
    as.data.frame() %>% 
    select(tech = adopted_pay_or_ecom_before_2019, Ebay_tradable, China_E_commerce, cons_BEC, durable_BEC) %>% 
    na.omit() %>% 
    summarize_all(list(Mean = mean)) %>% 
    pivot_longer(cols = everything(), 
                 names_to = c("variable", "statistic"),
                 names_pattern = "([A-Za-z_]+)_(Mean)") %>% 
    select(-statistic) %>% 
    mutate(across(where(is.numeric), round, 3)) %>% 
    pivot_wider(names_from = variable, 
                values_from = value)
    ) %>% 
  bind_rows(
    # India Exports
    export_mitig_data_IND %>% 
    as.data.frame() %>% 
    select(tech = adopted_pay_or_ecom_before_2019, Ebay_tradable, China_E_commerce, cons_BEC, durable_BEC) %>% 
    na.omit() %>% 
    summarize_all(list(Mean = mean)) %>% 
    pivot_longer(cols = everything(), 
                 names_to = c("variable", "statistic"),
                 names_pattern = "([A-Za-z_]+)_(Mean)") %>% 
    select(-statistic) %>% 
    mutate(across(where(is.numeric), round, 3)) %>% 
    pivot_wider(names_from = variable, 
                values_from = value) %>% 
    bind_rows(
      # India Imports
      import_mitig_data_IND %>% 
      as.data.frame() %>% 
      select(tech = adopted_pay_or_ecom_before_2019, Ebay_tradable, China_E_commerce, cons_BEC, durable_BEC) %>% 
      na.omit() %>% 
      summarize_all(list(Mean = mean)) %>% 
      pivot_longer(cols = everything(), 
                   names_to = c("variable", "statistic"),
                   names_pattern = "([A-Za-z_]+)_(Mean)") %>% 
      select(-statistic) %>% 
      mutate(across(where(is.numeric), round, 3)) %>% 
      pivot_wider(names_from = variable, 
                  values_from = value)
      )
      
  )

```


```{r, eval = T}

prods_tech<-as.data.frame(prods_tech)
rownames(prods_tech)<-c("Exports", "Imports", "Exports ", "Imports ")
colnames(prods_tech)<-c("Pre-2019\nE-payment/E-commerce", "e-Bay tradable", "China E-commerce", "Consumable", "Durable")

kbl(prods_tech, 
    caption = "Proportion of Observations with Dummy Variables Equal to 1 for E-payment/E-commerce adopted before 2019, e-Bay Tradable, China E-commerce, Consumable, and Durable Product Categories - Regression Sample", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Indonesia", 1, 2) %>%
  pack_rows("India", 3, 4)


```




```{r, eval=T}

stringency_index<-
  # Indonesia
  export_mitig_data_IDN %>% 
  as.data.frame() %>% 
  select(month_mean_stringency_index) %>% 
  summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd)) %>% 
    bind_rows(import_mitig_data_IDN %>% 
                as.data.frame() %>% 
                select(month_mean_stringency_index) %>% 
                summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, 
                                   Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd))
              )%>% 
    mutate(across(where(is.numeric), round, 2)) %>% 
  # India
    bind_rows(export_mitig_data_IND %>% 
      as.data.frame() %>% 
      select(month_mean_stringency_index) %>% 
      summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd)) %>% 
      bind_rows(import_mitig_data_IND %>% 
                  as.data.frame() %>% 
                  select(month_mean_stringency_index) %>% 
                  summarize_all(list(Min=min, p25 = ~quantile(., 0.25), Median = median, 
                                     Mean = mean, p75 = ~quantile(., 0.75), Max = max, SD = sd))
                )%>% 
      mutate(across(where(is.numeric), round, 2)) 
    )
  

rownames(stringency_index)<-c("Exports", "Imports", "Exports ", "Imports ")

kbl(stringency_index, 
    caption = "Descriptive Statistics of Monthly Average Stringency Index (Filling with 0s before 2020)", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  pack_rows("Indonesia", 1, 2) %>%
  pack_rows("India", 3, 4)

```


```{r, eval = T}

# It would also be useful to know how many exporting firms or importing firms are part of the sample.

n_firms<-
  # Indonesia Exports
  export_mitig_data_IDN %>% 
  as.data.frame() %>% 
  distinct(company_id) %>% 
  summarize(`Exporting Firms` = n()) %>% 
  # Indonesia Imports 
  bind_cols(
   import_mitig_data_IDN %>% 
    as.data.frame() %>% 
    distinct(company_id) %>% 
    summarize(`Importing Firms` = n()) 
  ) %>% 
  # India Exports
  bind_cols(export_mitig_data_IND %>% 
    as.data.frame() %>% 
    distinct(company_id) %>% 
    summarize(`Exporting Fimrs` = n())
    ) %>% 
  # India Imports
   bind_cols(import_mitig_data_IND %>% 
    as.data.frame() %>% 
    distinct(company_id) %>% 
    summarize(`Importing Fimrs` = n())
  ) %>% 
  mutate(across(everything(), big_number_format))
  
  


kbl(n_firms, 
    caption = "Number of Importing and Exporting Firms - Regression Sample", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  add_header_above(c("Indonesia" = 2, "India" = 2))

```


# Regression Samples for Extensive Margin 


## Regression Sample Extensive Margin: Does Tech Adoption Affect Trade Outcomes?


```{r}

rm(list = ls())
big_number_format<-function(x){format(x, big.mark = ",")}


import_data_IDN<-read_parquet(paste0("../../Data/Indonesia/processed_data/imports_grid_product_model_IDN.parquet"),
                            col_select = c("Ebay_tradable", "China_E_commerce", "cons_BEC", "durable_BEC",
                                           "company_id", "hs6", "date_character", "import_dummy",
                                           "pay_or_ecomnod_t_2"))


export_data_IDN<-read_parquet(paste0("../../Data/Indonesia/processed_data/exports_grid_product_model_IDN.parquet"),
                            col_select = c("Ebay_tradable", "China_E_commerce", "cons_BEC", "durable_BEC",
                                           "company_id", "hs6", "date_character", "export_dummy",
                                           "pay_or_ecomnod_t_2"))


import_data_IND<-read_parquet("../../Data/India/processed_data/imports_grid_product_model_IND.parquet",
                            col_select = c("Ebay_tradable", "China_E_commerce", "cons_BEC", "durable_BEC",
                                           "company_id", "hs6", "date_character", "import_dummy",
                                           "pay_or_ecomnod_t_2"))


export_data_IND<-read_parquet("../../Data/India/processed_data/exports_grid_product_model_IND.parquet",
                            col_select = c("Ebay_tradable", "China_E_commerce", "cons_BEC", "durable_BEC",
                                           "company_id", "hs6", "date_character", "export_dummy",
                                           "pay_or_ecomnod_t_2"))

```

```{r, eval = T}

prop_zeros<-
  export_data_IDN %>% 
  summarize(Exports = 1-mean(export_dummy)) %>% 
  as.data.frame() %>% 
  bind_cols(
    import_data_IDN %>% 
      summarize(Imports = 1-mean(import_dummy)) %>% 
      as.data.frame()
  ) %>% 
  bind_cols(
    export_data_IND %>% 
    summarize(Exports = 1-mean(export_dummy)) %>% 
    as.data.frame() %>% 
    bind_cols(
      import_data_IND %>% 
        summarize(Imports = 1-mean(import_dummy)) %>% 
        as.data.frame()
    )
  ) %>% 
  mutate(across(where(is.numeric), round, 3))


colnames(prop_zeros)<-c("Exports", "Imports", "Exports", "Imports")

 
kbl(prop_zeros, 
    caption = "Proportion of 0s in binary dependent variable in the expanded datasets", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  add_header_above(c("Indonesia Expanded Datasets" = 2, "India Expanded Datasets" = 2))
 
  




```


## Regression Sample Extensive Margin: Does Existing Tech Use Mitigate COVID Impacts?


```{r}

rm(list = ls())

import_data_IDN<-read_parquet("../../Data/Indonesia/processed_data/imports_grid_mitig_model_IDN.parquet",
                            col_select = c("Ebay_tradable", "China_E_commerce", "cons_BEC", "durable_BEC",
                                           "company_id", "hs6", "date_character", "import_dummy",
                                           "pay_or_ecomnod_t_2"))


export_data_IDN<-read_parquet("../../Data/Indonesia/processed_data/exports_grid_mitig_model_IDN.parquet",
                            col_select = c("Ebay_tradable", "China_E_commerce", "cons_BEC", "durable_BEC",
                                           "company_id", "hs6", "date_character", "export_dummy",
                                           "pay_or_ecomnod_t_2"))


import_data_IND<-read_parquet("../../Data/India/processed_data/imports_grid_mitig_model_IND.parquet",
                            col_select = c("Ebay_tradable", "China_E_commerce", "cons_BEC", "durable_BEC",
                                           "company_id", "hs6", "date_character", "import_dummy",
                                           "pay_or_ecomnod_t_2"))


export_data_IND<-read_parquet("../../Data/India/processed_data/exports_grid_mitig_model_IND.parquet",
                            col_select = c("Ebay_tradable", "China_E_commerce", "cons_BEC", "durable_BEC",
                                           "company_id", "hs6", "date_character", "export_dummy",
                                           "pay_or_ecomnod_t_2"))

```

```{r, eval = T}

prop_zeros<-
  export_data_IDN %>% 
  summarize(Exports = 1-mean(export_dummy)) %>% 
  as.data.frame() %>% 
  bind_cols(
    import_data_IDN %>% 
      summarize(Imports = 1-mean(import_dummy)) %>% 
      as.data.frame()
  ) %>% 
  bind_cols(
    export_data_IND %>% 
    summarize(Exports = 1-mean(export_dummy)) %>% 
    as.data.frame() %>% 
    bind_cols(
      import_data_IND %>% 
        summarize(Imports = 1-mean(import_dummy)) %>% 
        as.data.frame()
    )
  ) %>% 
  mutate(across(where(is.numeric), round, 3))


colnames(prop_zeros)<-c("Exports", "Imports", "Exports", "Imports")

 
kbl(prop_zeros, 
    caption = "Proportion of 0s in binary dependent variable in the expanded datasets", centering = T, booktabs = T, align = "c") %>%
  kable_classic() %>%
  kable_styling(latex_options = "HOLD_position") %>% 
  add_header_above(c("Indonesia Expanded Datasets" = 2, "India Expanded Datasets" = 2))
 
  

```



